Categorical and gradient aspects of wordlikeness\thanks{Thanks to Gene Buckley, Charles Yang, and audiences at NELS 43 for helpful comments.}

### 2012-11-11 3.tex
Completed writing on 2-4!

\section{Conclusions}

It has been shown that statistical reliability is not a sufficient condition for a sequence structure generalization to be reflected in psycholinguistic tasks. However, in the case of constraints on Turkish vowels, it is a necessary condition that the constraint in question be derived from an alternation. Even alternations that have large numbers of lexical exceptions have robust effects on a constrained wordlikeness task. Purely statistical approaches to phonotactic knowledge fail to draw this important distinction.

>>>>

\section{Conclusion}

Statistical reliability is not a sufficient condition for a sequence structure generalization internalized by speakers or reflected in psycholinguistic tasks. This case suggests that it is a necessary condition that the constraint in question be derived from an alternation, however. Even alternations that have large numbers of lexical exceptions have robust effects on a constrained wordlikeness task. Purely statistical approaches to phonotactic knowledge fail to draw the distinction between static and derived phonotactic generalizations.
